A reproduction of Newspapers in Times of Low Advertising Revenues

### 2020-12-22 Outputs/Paper/Paper.Rmd
update quality aspect

I will use the natural log of the value of the outcome of interest instead while modeling the dataset. This is so that the outcome value will be smaller. The equation is as follows:  
\begin{equation}
\ln{(y_{n,t})} = \alpha + \beta_{1}(D_\text{after} * D_\text{national news}) + \lambda_{n} + \gamma_{t} + \epsilon_{n,t}
(\#eq:2)
\end{equation}

We want to investigate the different models to look at effects on the advertising side, reader side and the quality of the newspapers based on equation \@ref(eq:2).

@@

>>>>

I will use the natural log of the value of the outcome of interest instead while modeling the dataset. This is so that the outcome value will be smaller. This will make equation \@ref(eq:1) similar to equation \@ref(eq:2) with the y value scaled by natural log. The equation is as follows:  
\begin{equation}
\ln{(y_{n,t})} = \alpha + \beta_{1}(D_\text{after} * D_\text{national news}) + \lambda_{n} + \gamma_{t} + \epsilon_{n,t}
(\#eq:2)
\end{equation}

We want to investigate the different models to look at effects on the advertising side, reader side and the quality of the newspapers based on equation \@ref(eq:2). $\beta_{1}$ is the difference in difference value which we are interested in.

@@

```{r tab3}
newspapers$id_news <- as.factor(newspapers$id_news)
journalists <- lm(log(nb_journ) ~ after_national + id_news + year, data = newspapers)
ave_payroll <- lm(ln_av_payroll_cst ~ after_national + id_news + year, data = newspapers)
pages <- lm(ln_pages ~ after_national + id_news + year, data = newspapers)
news_hole <- lm(ln_news_hole ~ after_national + id_news + year, data = newspapers)
share_hard_news <- lm(share_Hard ~ after_national + id_news + year, data = newspapers)

hx<-huxreg("journalists" = journalists, 
       "payroll" = ave_payroll, 
       "of pages" = pages, 
       "Newshole" = news_hole,
       "on front page (percent)" = share_hard_news,
       omit_coefs = omit_me, 
       number_format = 2
       )
insert_row(hx,c("","Number of","Average","Number","","Share of hard news"),after=0) %>%
set_caption("Quality") %>%
set_text_color(3,2:6, "red")
